\vspace{1.0cm} \LARGE \bf Structured population models demystify MERS-CoV epidemiology

### 2017-07-14 mers-structure.tex
Minor fix to algorithm.

\begin{algorithm}[H]
 \KwData{Array of case cluster sizes in outbreak $\boldsymbol C = [C_{1},C_{2}, \ldots, C_{K}]$, sequences available $M$, total outbreak size $\sum_{i=1}^{K} C_{i}$.}
 \KwResult{Array of sequence cluster sizes sampled: $\boldsymbol S = [S_{1},S_{2}, \ldots, S_{K}]$.}
 Draw $S_{i}$ from a hypergeometric distribution with $C_{i}$ successes, $\sum_{i=1}^{K} C_{i}-C_{i}$ failures after $M$ trials\;
 \While{$i < K$}{
  $i = i + 1$\;
  $M = M - S_{i-1}$\;
  Compute the probability mass function (pmf) for all possible values of $S_i$, $\boldsymbol p = [p(0)^{\text{bias}}, p(1), \ldots, p(C_{i})^{\text{bias}}] \times (\sum_i p_i^{\text{bias}}) ^{-1}$, where $p(\cdot)$  is the pmf for a hypergeometric distribution with $C_{i}$ successes, $\sum_{i=1}^{K} C_{i}-C_{i}$ failures after $M$ trials\;
  Draw a sequence cluster size $S_{i}$ from array of potential sequence cluster sizes $[0, 1, \ldots, C_{i}]$ according to $\boldsymbol p$\;
 }
 Add remaining sequences to last sequence cluster $C_{K} = M - S_{K-1}$\;
 \caption{\textbf{Multivariate hypergeometric sampling scheme.}
 Pseudocode describes the multivariate hypergeometric sampling scheme that simulates sequencing.
 Probability of sequencing a given number of cases from a case cluster depends on cluster size and sequences left (\textit{i.e.} ``sequencing capacity'').
 The bias parameter determines how probability mass function of the hypergeometric distribution is concentrated.
 }
 \label{hypergeometric}
\end{algorithm}

>>>>

\begin{algorithm}[H]
 \KwData{Array of case cluster sizes in outbreak $\boldsymbol C = [C_{1},C_{2}, \ldots, C_{K}]$, sequences available $M$, total outbreak size $\sum_{i=1}^{K} C_{i}$.}
 \KwResult{Array of sequence cluster sizes sampled: $\boldsymbol S = [S_{1},S_{2}, \ldots, S_{K}]$.}
 Draw $S_{i}$ from a hypergeometric distribution with $C_{i}$ successes, $\sum_{i=1}^{K} C_{i}-C_{i}$ failures after $M$ trials\;
 \While{$i < K$}{
  $i = i + 1$\;
  $M = M - S_{i-1}$\;
  Compute the probability mass function (pmf) for all possible values of $S_i$, $\boldsymbol p = [p(0)^{\text{bias}}, p(1)^{\text{bias}}, \ldots, p(C_{i})^{\text{bias}}] \times (\sum_i p_i^{\text{bias}}) ^{-1}$, where $p(\cdot)$  is the pmf for a hypergeometric distribution with $C_{i}$ successes, $\sum_{i=1}^{K} C_{i}-C_{i}$ failures after $M$ trials\;
  Draw a sequence cluster size $S_{i}$ from array of potential sequence cluster sizes $[0, 1, \ldots, C_{i}]$ according to $\boldsymbol p$\;
 }
 Add remaining sequences to last sequence cluster $C_{K} = M - S_{K-1}$\;
 \caption{\textbf{Multivariate hypergeometric sampling scheme.}
 Pseudocode describes the multivariate hypergeometric sampling scheme that simulates sequencing.
 Probability of sequencing a given number of cases from a case cluster depends on cluster size and sequences left (\textit{i.e.} ``sequencing capacity'').
 The bias parameter determines how probability mass function of the hypergeometric distribution is concentrated.
 }
 \label{hypergeometric}
\end{algorithm}
